A thesis draft

### 2018-11-15 res/sections/25-Tests.tex
Little fix

\noindent As is possible to see from the YAML definition, the test involved, for
every launch, the VNF download from the Docker hub repositories. This, while it
forced every node to delete and download the image for each test, it ensured
consistent measurements in cases where the selected node for the deployment did
not have the image already pulled. In addition to that, another consideration
needs to be taken into account: when the chain consists of two or more elements,
the container image which is used for the container deployment is the same for
every VNF involved, thus reducing the start up time for the subsequent pods that
reside in nodes that have already deployed one.

>>>>

\noindent As is possible to see from the YAML definition, the test involved, for
every launch (that included and $N = 100$, for a total for 1000 tests), the VNF
download from the Docker hub repositories. This, while it forced every node to
delete and download the image for each test, it ensured consistent measurements
in cases where the selected node for the deployment did not have the image
already pulled. In addition to that, another consideration needs to be taken
into account: when the chain consists of two or more elements, the container
image which is used for the container deployment is the same for every VNF
involved, thus reducing the start up time for the subsequent pods that reside in
nodes that have already deployed one.
